Online Multiclass Linear Classification with Bandit Feedback

### 2018-12-20 arxiv-version/main.tex
Small fix

In this section, we show how to construct a mapping $\phi$ from the unit
ball of $\R^d$ into a high dimensional inner product space that has the
property if a set of labeled examples in the unit ball is linearly separable with a
margin $\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
the number of classes $K$, and the are specified in the theorems below.

>>>>

In this section, we show how to construct a mapping $\phi$ from the unit ball of
$\R^d$ into a high dimensional inner product space that has the property that if
a set of labeled examples in the unit ball is linearly separable with a margin
$\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
the number of classes $K$, and the are specified in the theorems below.
